Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-06-25 manuscript/manuscript.Rmd
added new ref

Difficulty establishing the analytic reproducibility of research reports has been encountered in several scientific domains, including economics, political science, and psychology [@chang2015; @eubank2016; @stodden2018; @obels2019; @hardwicke2018a; but see @naudet2018]. A preliminary obstacle for many such studies is that research data are typically unavailable [@hardwicke2018; @hardwicke2020a; @wicherts2006]. Even when data can be accessed, suboptimal management and inadequate documentation can complicate data reuse [@hardwicke2018a; @kidwell2016]. These failures to adequately preserve and share earlier stages of the research pipeline typically preclude downstream assessment of analytic reproducibility.

>>>>

Difficulty establishing the analytic reproducibility of research reports has been encountered in several scientific domains, including economics, political science, behavioural ecology, and psychology [@chang2015; @eubank2016; @stodden2018; @obels2019; @hardwicke2018a; @minocher2020; but see @naudet2018]. A preliminary obstacle for many such studies is that research data are typically unavailable [@hardwicke2018; @hardwicke2020a; @wicherts2006]. Even when data can be accessed, suboptimal management and inadequate documentation can complicate data reuse [@hardwicke2018a; @kidwell2016]. These failures to adequately preserve and share earlier stages of the research pipeline typically preclude downstream assessment of analytic reproducibility.
